A Makefile for Developing Containerized \LaTeX\ Technical Documents

### 2021-01-04 ms.tex
remove unused package in ms.tex
fix

\documentclass[journal]{IEEEtran}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usepackage[hyphens]{url}
\usepackage{hyperref}

@@

The \textit{author} may use the Makefile for developing \textit{documents} in the following way:
\begin{enumerate}
	\item clones/downloads the template repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:templatefiles},
	\item specifies the name of the \textit{document} in the Makefile,
	\item creates and develops the \textit{results code}.
	\item creates and develops the \textit{\LaTeX\ code}.
	\item executes \textit{make} for fast development iterations and experimentation,
	\item executes \textit{make VER=-{}-full} for distribution or publication and
	\item executes \textit{make clean} to restore to a clean state.
\end{enumerate}

@@

\section*{Conclusion}
Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
The proposed Makefile aids to this purpose by providing a way to write reproducible technical documents using the standard tools that many of the academics already use (\LaTeX, Docker, Make) in a portable, efficient and future-proof way.

>>>>

\documentclass[journal]{IEEEtran}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usepackage{hyperref}

@@

The \textit{author} may use the Makefile for developing \textit{documents} in the following way:
\begin{enumerate}
	\item clones/downloads the template repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:templatefiles},
	\item creates and develops the \textit{results code}.
	\item creates and develops the \textit{\LaTeX\ code}.
	\item executes \textit{make} for fast development iterations and experimentation,
	\item executes \textit{make VER=-{}-full} for distribution or publication and
	\item executes \textit{make clean} to restore to a clean state.
\end{enumerate}

@@

\section*{Conclusion}
The proposed Makefile aids to this purpose by providing a way to write reproducible technical documents using the standard tools that many of the academics already use (\LaTeX, Docker, Make) in a portable, efficient and future-proof way.
